Prefetching SPARQL query cacher

### 2016-05-04 dissertation/introdefhistory.tex

The following challenges several conventions of scientific
writing. Passive voiced is generally overused in scientific writing,
sometimes because the author may think it emphasises the objectivity
of the investigation. In my opinion it rather attempts to hide the
fact that science is a human and social endeavour, and only by
acknowledging that fact, an investigator can properly account for
their own role. Double blind trials in medicine are an example of why
it is important to acknowledge the investigators role. Moreover, the
use of ``we'', when it is clear that the work has been done by a
single investigator is inappropriate as it obscures
the role of the investigator.

As noted, the Semantic Web is a complex technical, social, economic
and cultural artefact. The objectivity of an investigator may be
challenged by a large intellectual investment in this artefact, the
more you want this artefact to succeed, the higher may your risk of not
being sufficiently objective be. I hereby declare that I have a very
large intellectual investment in the success of the Semantic Web, and
therefore this section is a reflection on my own role in the
development of this artefact.

@@

While the motivation and the problem statements of this work
undoubtedly have been influenced by my intellectual investment in the
Semantic Web, the papers will show that the evaluation has not.

>>>>

The following challenges several conventions of scientific
writing. Passive voice is generally overused in scientific writing,
sometimes because the author may think it emphasises the objectivity
of the investigation. In my opinion it rather attempts to hide the
fact that science is a human and social endeavour, and only by
acknowledging that fact, an investigator can properly account for
their own role. Double blind trials in medicine are an example of why
it is important to acknowledge the investigator's role. Moreover, the
use of ``we'', when it is clear that the work has been done by a
single investigator is inappropriate as it obscures
the role of the investigator.

As noted, the Semantic Web is a complex technical, social, economic
and cultural artefact. The objectivity of an investigator may be
challenged by a large intellectual investment in this artefact, the
more you want this artefact to succeed, the higher may your risk of
not being sufficiently objective be. I hereby declare that I have a
very large intellectual investment in the success of the Semantic Web,
and therefore this section is a reflection on my own role in the
development of this artefact. This serves to clarify \emph{my} vision
as well as aspects that may influence the objectivity of the
investigation.

@@

While the motivation and the problem statements of this work
undoubtedly have been influenced by my intellectual investment in the
Semantic Web, the papers should show that the investigation has not.

### 2016-05-04 dissertation/problems.tex
Discuss the SIGMOD paper on caching

Problem~\ref{prob:badphil} has been a growing concern throughout this
work. A proper evaluation should be an important part of the
dissertation, and yet, the problems discussed in
Section~\ref{sec:evalproblems} are so severe that the time frame of
this work does not allow a satisfactory solution to these
problems. The paper discussed in Section~\ref{sec:conphil} serves to
excuse this.

@@

Problem~\ref{prob:queryeq} is best addressed by creating hashing
algorithms that have a reasonable chance of returning the same digest
if two queries are equivalent. Some works have created cryptographical
hashing functions, but they may be overly costly to compute for this
purpose. % TODO ref.

>>>>

Problem~\ref{prob:badphil} has been a growing concern throughout this
work. A proper evaluation should be an important part of the
dissertation, and yet, the problems discussed in
Section~\ref{sec:evalproblems} are so severe that the time frame of
this work does not allow a satisfactory solution to these
problems. The paper discussed in Section~\ref{sec:conphil} is
motivated in part from these problems.

@@

Problem~\ref{prob:queryeq} is best addressed by creating hashing
algorithms that have a reasonable chance of returning the same digest
if two queries are equivalent. This problem was addressed by
\cite{papailiou2015graph} and their approach might be portable to be
used in an HTTP context.
